|

### 2018-11-27 S4_qPLEX-RIME_GRHL2/rRunTMTanalysis.Rmd
removed master document to reduce complexity

# fasta file of protein sequence
fastaFile <- paste0("accessoryFiles/", UniProtAccession, ".fasta")
fastaUrl <- paste0("http://www.uniprot.org/uniprot/", UniProtAccession, ".fasta")
download.file(fastaUrl, fastaFile, "wget")

@@

```{r coveragePlot, echo=F, fig.width=10, fig.height=2, fig.cap=covCap, results="asis"}
covCap <- refcaption("covFig", paste0("Plot of peptide coverage for ", baitProtein, " (UniprotID: ", UniProtAccession, ")"))
coveragePlot2(data=rawMSnset, ProteinID=UniProtAccession, ProteinName=baitProtein, fastaFile=fastaFile)
```

>>>>

# fasta file of protein sequence
fastaFile <- paste0("accessoryFiles/", UniProtAccession, ".fasta")
fastaUrl <- paste0("http://www.uniprot.org/uniprot/", UniProtAccession, ".fasta")
download.file(fastaUrl, fastaFile)

@@

```{r coveragePlot, echo=F, fig.width=10, fig.height=2, fig.cap=covCap, results="asis"}
covCap <- refcaption("covFig", paste0("Plot of peptide coverage for ", baitProtein, " (UniprotID: ", UniProtAccession, ")"))
#colnames(fData(rawMSnset))[6]<-"Master.Protein.Accessions"
coveragePlot2(data=rawMSnset, ProteinID=UniProtAccession, ProteinName=baitProtein, fastaFile=fastaFile)
```
